%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Ahmad Abdulrahman Radwan} \\ \vspace{1pt}
    \small +20 114 923 1141 $|$ \href{mailto:ah.abdulrahmaan@gmail.com}{\underline{ah.abdulrahmaan@gmail.com}} $|$ 
    \href{https://linkedin.com/in/ahmad-abdulrahmaan}{\underline{linkedin.com/in/ahmad-abdulrahmaan}} $|$
    \href{https://github.com/AHR9N}{\underline{github.com/AHR9N}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Faculty of Engineering, Al-Azhar University}{Cairo, Egypt}
      {Bachelor of Systems and Computer Engineering}{Sep. 2017 -- Expected: Jul. 2022}
  \resumeSubHeadingListEnd

%-----------PROBLEM SOLVING COMPETITIONS & ACHIEVEMENTS-----------
\section{Problem Solving Competitions}
    \resumeItemListStart
        \resumeItem{\textbf{Ranked 12th} on Egypt in Google HashCode 2021.}
        \resumeItem{\textbf{Finalist} in Africa \& Arab Collegiate Programming Contest (ACPC) 2020.}
        \resumeItem{\textbf{Ranked 45th} in Egyptian Collegiate Programming Contest (ECPC) 2020.}
        \resumeItem{\textbf{Ranked 4th} on Egypt in IEEEXtreme 14.0 Programming Competition.}
        \resumeItem{\textbf{Solved +1300 various problems} on several online judges, (Codeforces, UVa, SPOJ, LeetCode, ..etc).}
        \resumeItem{\textbf{Expert} on Codeforces, handle: \href{https://codeforces.com/profile/RetiredRadwan}{\underline{RetiredRadwan}}.}
      \resumeItemListEnd

%-----------EXPERIENCE & VOLUNTEERING-----------
\section{Experience \& Volunteering}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Mentor \& Problem-setter}{Feb. 2020 -- Present}
      {AIC - Al-Azhar ICPC Community}{Cairo, Egypt}
      \resumeItemListStart
        \resumeItem{Teaching topics, popular algorithms and techniques of competitive programming.}
        \resumeItem{Helping write problem-sets for weekly sheets and contests.}
    \resumeItemListEnd

    \resumeSubheading
      {Social Media Specialist}{Feb. 2020 -- Present}
      {AIC - Al-Azhar ICPC Community}{Cairo, Egypt}
      \resumeItemListStart
        \resumeItem{Using social media platforms to connect with trainees to build and organize the training step by step, involving publishing all content about competitive programming.}
      \resumeItemListEnd

    \resumeSubheading
      {Radio/Phonetics Committee Member}{Nov. 2020 -- Present}
      {MOIC ASU - Model Organization Of Islamic Co-operation}{Cairo, Egypt}
      \resumeItemListStart
        \resumeItem{Helping provide Arabic voice-overs involved in media posts about educating students of current trends in theory and practice of international relations, effective communication and
multilateral diplomacy.}
      \resumeItemListEnd
      
      \resumeSubheading
      {Radio/Phonetics Committee Member}{Apr. 2019 -- Jun. 2019}
      {MOIC ASU - Model Organization Of Islamic Co-operation}{Cairo, Egypt}
      \resumeItemListStart
        \resumeItem{Helped provide Arabic calligraphy and typography designs involved in posts about
educating students of current trends in relations, communication.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Notify Me!} $|$ \emph{JavaScript, HTML}}{Jan. 2021}
          \resumeItemListStart
            \resumeItem{Developed a full-stack web browser extension which notifies contestants when there are announcements on \href{https://vjudge.net/}{\underline{VJudge OJ}} running contests, instead of wasting time reloading pages and looking for them periodically.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{In The Queue, Please!} $|$ \emph{Java, JavaFX GUI, CSS}}{Dec. 2022}
          \resumeItemListStart
            \resumeItem{Implemented the Deterministic and Stochastic Models in Queuing Theory, including showing graph result (if exists for a model).}
          \resumeItemListEnd
       \resumeProjectHeading
          {\textbf{Differentiation Lab} $|$ \emph{Java}}{May. 2019}
          \resumeItemListStart
            \resumeItem{Implemented a calculator that allows you to solve first order and higher order derivatives of any function using Apache exp4j library, based on GUI.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, Java, Kotlin, Python, JavaScript, HTML/CSS} \\
     \textbf{Tools \& Technologies}{: Unix/Linux, Git, CLion, IntelliJ, PyCharm, Android} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
